---
title: "Final_ASL"
author: "21BDA07, 21BDA11, 21BDA54"
date: "05/07/2022"
output: pdf_document
---
 ADVANCED STATISTICS LAB PROJECT 
 SEMESTER 2
 MSC. BIG DATA ANALYTICS 
 _______________________________________________________
 Angel Philip - 21BDA07
 Jerusha Gomez - 21BDA11
 Lakshitha Sethi - 21BDA54
 
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Importing the required libraries:

```{r}
library(dplyr)
library(funModeling)
library(Hmisc)
library(ggplot2)
library(scales)
library(RColorBrewer)
library(party)
library(InformationValue)
library(pROC)
```

2. Loading the data:

```{r}
dataset <- read.csv("LeadScoring.csv")
dim(dataset)
```

3. Taking a look at the data:

```{r}
ncol(dataset)
nrow(dataset)
summary(dataset)
str(dataset)
```

4. Data Cleaning

```{r}
#Filling the missing values with NA
dataset[dataset == ""] <- NA 

#Finding the total number of missing values
sum(is.na(dataset))

#Finding the missing value count per column
sapply(dataset, function(x) sum(is.na(x)))

#Narrowing data down to just Indian Leads
ind_data <- dataset[dataset$Country == 'India',]

#Removing the entries with country as NA
new_data <- subset(ind_data,!is.na(ind_data$Country))

#Keeping the converted value as character for further visualizations.
new_data$Converted <- as.factor(new_data$Converted)
View(new_data)
#Removing unnecessary columns
new_data_1 <- new_data[-c(1,16:24,27,28,35,36)]
View(new_data_1)

#Imputation of missing numerical values
new_data_1$Asymmetrique.Activity.Score[is.na(new_data_1$Asymmetrique.Activity.Score)]<-mean(new_data_1$Asymmetrique.Activity.Score,na.rm=TRUE)
new_data_1$Asymmetrique.Profile.Score[is.na(new_data_1$Asymmetrique.Profile.Score)]<-mean(new_data_1$Asymmetrique.Profile.Score,na.rm=TRUE)

#Renaming Column Names
new_data_1 <- rename(new_data_1, Time.on.Web=Total.Time.Spent.on.Website)
new_data_1 <- rename(new_data_1, Hear.About=How.did.you.hear.about.X.Education)
new_data_1 <- rename(new_data_1, Occupation=What.is.your.current.occupation)

#Cleaning the Specialization Column
dplyr::count(new_data_1, new_data_1$Specialization, sort = TRUE)

#Imputing with random values of the same column
new_data_1$Specialization <- with(new_data_1,impute(new_data_1$Specialization,"random"))
new_data_1$Hear.About <- with(new_data_1,impute(new_data_1$Hear.About,"random"))
new_data_1$Occupation <- with(new_data_1,impute(new_data_1$Occupation,"random"))
new_data_1$Tags <- with(new_data_1,impute(new_data_1$Tags,"random"))
new_data_1$Lead.Quality <- with(new_data_1,impute(new_data_1$Lead.Quality,"random"))
new_data_1$Lead.Profile <- with(new_data_1,impute(new_data_1$Lead.Profile,"random"))
new_data_1$City <- with(new_data_1,impute(new_data_1$City,"random"))
new_data_1$Asymmetrique.Activity.Index <- with(new_data_1,impute(new_data_1$Asymmetrique.Activity.Index,"random"))
new_data_1$Asymmetrique.Profile.Index <- with(new_data_1,impute(new_data_1$Asymmetrique.Profile.Index,"random"))

new_data_1 <- subset(new_data_1,!is.na(new_data_1$Lead.Source))
```


5. Exploratory Data Analysis

```{r}
#Snapshot of the data
glimpse(new_data_1)
status(new_data_1)
```
```{r}
#1.Percentage of Converted
conv <- new_data_1 %>% 
  group_by(new_data_1$Converted) %>% # Variable to be transformed
  count() %>% 
  ungroup() %>% 
  mutate(perc = `n` / sum(`n`)) %>% 
  arrange(perc) %>%
  mutate(labels = scales::percent(perc))
conv
conv <- rename(conv, Conversion.Rate = `new_data_1$Converted`)
plot1 <- ggplot(conv, aes(x = "", y = perc, fill = factor(Conversion.Rate))) +
  geom_col() + geom_text(aes(label = labels),position = position_stack(vjust = 0.5)) +
  coord_polar(theta = "y")+ylab("") + ggtitle("Percentage of Conversion") + theme(plot.title = element_text(hjust = 0.5))+ guides(fill=guide_legend(title=""))+ scale_fill_discrete( labels = c("Not Converted", "Converted"))
plot1
```
```{r}
#2. Lead Source Distribution
lead_source <- new_data_1 %>% 
  group_by(new_data_1$Lead.Source) %>% # Variable to be transformed
  count() %>% 
  ungroup() %>% 
  mutate(perc = `n` / sum(`n`)) %>% 
  arrange(perc) %>%
  mutate(labels = scales::percent(perc))           
lead_source <- rename(lead_source, Lead_Source = `new_data_1$Lead.Source`)
ls_2 <- head(arrange(lead_source,desc(lead_source$perc)), n = 5)

plot2 <- ggplot(data=ls_2, aes(x=reorder(Lead_Source,-perc), y=perc)) +
  geom_bar(stat="identity", color="black", fill="#C77CFF")+ ggtitle("Top 5 Lead Sources")+ theme(plot.title = element_text(hjust = 0.5))
plot2 <- plot2+geom_text(aes(label = labels),position = position_stack(vjust = 0.5))+xlab("Lead Source")+ylab("Percentage")
plot2
```
```{r}
#3. Average Time Spent On the Web 
max(new_data_1$Time.on.Web)
min(new_data_1$Time.on.Web)
mean(new_data_1$Time.on.Web)
median(new_data_1$Time.on.Web)
quantile(new_data_1$Time.on.Web)
#Conclusion - 10 minutes is the average time spent on the website
plot3 <- ggplot(new_data_1, aes(x = 1, y = Time.on.Web)) + geom_boxplot(position = position_dodge(preserve = "single"),fill='#CC9999', color="black") +
  xlab(NULL) + theme(axis.text.y = element_blank()) + coord_flip(ylim=c(0, 1400)) 
plot3 <- plot3 + ggtitle("Time Spent on the Website")+ theme(plot.title = element_text(hjust = 0.5))+ylab("Time (in seconds)")
plot3
```
```{r}
#4. Total visits to the website.
mean_visits <- mean(new_data_1$TotalVisits)
mean_visits
#Conclusion - there is an average of 4-5 visits per person

plot4 <- ggplot(new_data_1, aes(x=TotalVisits)) + 
  geom_histogram(binwidth=1,color="black", fill="grey") + xlim(0,30) 
plot4
```
```{r}
#5. Lead Origin Distribution
lead_og <- new_data_1 %>% 
  group_by(new_data_1$Lead.Origin) %>% # Variable to be transformed
  count() %>% 
  ungroup() %>% 
  mutate(perc = `n` / sum(`n`)) %>% 
  arrange(perc) %>%
  mutate(labels = scales::percent(perc))     
lead_og <- head(arrange(lead_og,desc(lead_og$perc)))
lead_og
plot5 <- ggplot(data=lead_og, aes(x=`new_data_1$Lead.Origin`, y=perc)) +
  geom_bar(stat="identity", color="blue", fill="blue")
plot5
#Conclusion - Landing page submission accounts for 70% of the leads.
```
```{r}
#6. Last Activity
last_act <- new_data_1 %>% 
  group_by(new_data_1$Last.Activity) %>% # Variable to be transformed
  count() %>% 
  ungroup() %>% 
  mutate(perc = `n` / sum(`n`)) %>% 
  arrange(perc) %>%
  mutate(labels = scales::percent(perc))     
last_act <- head(arrange(last_act,desc(last_act$perc)))
plot6 <- ggplot(data=last_act, aes(x=`new_data_1$Last.Activity`, y=perc)) +
  geom_bar(stat="identity", color="black", fill="black") + theme(axis.text.x = element_text(angle = 90))
plot6
#Conclusion - Email opened and SMS sent are the leading last activities.
```
```{r}
#7. Occupation
occu_table <-  new_data_1 %>% count(new_data_1$Occupation)
occu_table
plot7 <- ggplot(data=occu_table, aes(x=`new_data_1$Occupation`, y=n)) +
  geom_bar(stat="identity", color="blue", fill="blue") + scale_x_discrete()
plot7
```
```{r}
#8. Lead Origin and Converted Count
temp_tab <- new_data_1 %>% group_by(new_data_1$Lead.Origin,new_data_1$Converted) %>% summarise(sum_conv = n(),groups=NULL)
temp_tab
plot8 <- ggplot(temp_tab, aes(fill =`new_data_1$Converted`,group = `new_data_1$Converted`, y=sum_conv, x=`new_data_1$Lead.Origin`)) + 
  geom_bar(position="dodge", stat="identity")
plot8 <- plot8 + ylab("Number of Conversion") + xlab("Lead Origin")+ scale_fill_manual(values = c("#800000","#f5f5f5"))+theme_dark()
plot8
```
```{r}
# Lead Source and Converted
plot9 <- ggplot(new_data_1, aes(fill =Converted,group = Converted, y=TotalVisits, x=Lead.Source)) + 
  geom_bar(position="dodge", stat="identity") + theme(axis.text.x = element_text(angle = 90))
plot9

plot10 <- ggplot(new_data_1, aes(fill =Converted,group = Converted, y=Time.on.Web, x=Lead.Source)) + 
  geom_bar(position="dodge", stat="identity") + theme(axis.text.x = element_text(angle = 90))+ scale_x_discrete()+scale_fill_manual(values = c("#054C70","#05C3DE"))
plot10

plot11 <- ggplot(new_data_1, aes(fill =Lead.Origin,group = Lead.Origin, y=Time.on.Web, x=Converted)) + 
  geom_bar(position="dodge", stat="identity") + theme(axis.text.x = element_text(angle = 0))
plot11

plot12 <- ggplot(new_data_1, aes(fill = Converted,group = Converted, y=TotalVisits, x=Hear.About)) + 
  geom_bar(position="dodge", stat="identity") + theme(axis.text.x = element_text(angle = 90)) + scale_x_discrete()
plot12

plot13 <- ggplot(new_data_1, aes(fill = Converted,group = Converted, y=TotalVisits, x=Occupation)) + 
  geom_bar(position="dodge", stat="identity") + theme(axis.text.x = element_text(angle = 90)) + scale_x_discrete()+scale_fill_manual(values = c("#054C70","#05C3DE"))
plot13

plot14 <- ggplot(new_data_1, aes(fill = Converted,group = Converted, y=TotalVisits, x=Specialization)) + 
  geom_bar(position="dodge", stat="identity") + theme(axis.text.x = element_text(angle = 90)) + scale_x_discrete()
plot14

plot15 <- ggplot(new_data_1,aes(Specialization)) + geom_bar() + scale_x_discrete() + theme(axis.text.x = element_text(angle = 90))
plot15

plot16 <- ggplot(new_data_1, aes(fill = Lead.Origin,group = Lead.Origin, y=TotalVisits, x=Last.Activity)) + 
  geom_bar(position="dodge", stat="identity") + theme(axis.text.x = element_text(angle = 90)) + scale_x_discrete()
plot16
```
6. Modelling the Data
a) Checking for correlations

```{r}
# Performing chi square test for checking dependency of categorical variables.
chisq.test(new_data_1$Converted,new_data_1$Lead.Origin)
chisq.test(new_data_1$Converted,new_data_1$Lead.Source)
chisq.test(new_data_1$Converted,new_data_1$Do.Not.Email)
# seems to be highly correlated
chisq.test(new_data_1$Converted,new_data_1$Do.Not.Call)
# not at all correlated to the dependent variable
chisq.test(new_data_1$Converted,new_data_1$Specialization)
chisq.test(new_data_1$Converted,new_data_1$Hear.About)
chisq.test(new_data_1$Converted,new_data_1$Occupation)
#highly correlated
chisq.test(new_data_1$Converted,new_data_1$Lead.Profile)
#highly correlated
chisq.test(new_data_1$Converted,new_data_1$Tags)
#highly related
chisq.test(new_data_1$Converted,new_data_1$City)
chisq.test(new_data_1$Converted,new_data_1$Asymmetrique.Activity.Index)
chisq.test(new_data_1$Converted,new_data_1$Asymmetrique.Profile.Index)
#correlated to some extent
chisq.test(new_data_1$Converted,new_data_1$Last.Notable.Activity)
#highly correlated
chisq.test(new_data_1$Converted,new_data_1$Tags)
#highly correlated
chisq.test(new_data_1$Converted,new_data_1$Lead.Quality)
#highly correlated
```

b) Splitting data into test and train

```{r}
Sample <- sample(c(TRUE, FALSE), nrow(new_data_1), replace=TRUE, prob=c(0.7,0.3))
train <- new_data_1[Sample, ]
test <- new_data_1[!Sample, ] 
```

c) Fitting a Linear Regression Model

```{r}
#Linear Regression
#Creating the model
new_data_1$Converted <- as.numeric(as.character(new_data_1$Converted))
linear_model<-lm(Converted ~ Do.Not.Email+Occupation+Lead.Profile+Tags+Lead.Quality+Last.Notable.Activity, data = new_data_1)

#Visualizing the model
par(mfrow=c(2,2))
plot(linear_model)
par(mfrow=c(1,1))
#Viewing results
anova(linear_model)
summary(linear_model)
```
d) Predicting using the model:

```{r}
new_data_1$Lead.Score<- round((predict(linear_model)*100),0)
View(new_data_1)
```

e) Cleaning up some values to avoid confusion:

```{r}
#Checking the boundaries
max(new_data_1$Lead.Score)
min(new_data_1$Lead.Score)

#Computing median 
median(new_data_1$Lead.Score)

new_data_1$Lead.Score[new_data_1$Lead.Score < 0 ] <- 0 
new_data_1$Lead.Score[new_data_1$Lead.Score > 100] <- 100
```

f) Encoding the Lead Score into Hot and Cold leads:

```{r}
#Creating a column called Lead.Type
new_data_1$Lead.Type[new_data_1$Lead.Score <= 50] = 0
new_data_1$Lead.Type[new_data_1$Lead.Score > 50] = 1

```

g) Testing the model:

```{r}
error_value <- optimalCutoff(new_data_1$Converted, new_data_1$Lead.Type)[1]
error_value
```
7. Logistic Regression 

```{r}
lr_model <- glm(Lead.Type ~ Lead.Score, family=binomial(logit), data=new_data_1)
summary(lr_model)
View(new_data_1)
```

Thank you!
__________________________________________________________________________
